Supplementary Appendix

### 2025-07-23 paper/preprint/appendix.tex
one final note on random seeds in appendix

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-train-default}: Training Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-eval-default}: Evaluation Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-train-final-run-train}: Training Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-tune-train}: Training Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-tune-eval}: Evaluation Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-tune_lr-train}: Training Phase}, bottomrule=.15mm, toptitle=1mm]

@@

\begin{tcolorbox}[enhanced jigsaw, toprule=.15mm, colbacktitle=quarto-callout-note-color!10!white, colframe=quarto-callout-note-color-frame, rightrule=.15mm, left=2mm, coltitle=black, colback=white, breakable, leftrule=.75mm, bottomtitle=1mm, arc=.35mm, opacityback=0, titlerule=0mm, opacitybacktitle=0.6, title={Note \ref*{nte-tune_lr-eval}: Evaluation Phase}, bottomrule=.15mm, toptitle=1mm]

@@

We have taken care to set random seeds for reproducibility.

>>>>

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, left=2mm, opacitybacktitle=0.6, breakable, titlerule=0mm, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-train-default}: Training Phase}, coltitle=black, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, toprule=.15mm, opacityback=0, colback=white]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, left=2mm, opacitybacktitle=0.6, breakable, titlerule=0mm, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-eval-default}: Evaluation Phase}, coltitle=black, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, toprule=.15mm, opacityback=0, colback=white]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, left=2mm, opacitybacktitle=0.6, breakable, titlerule=0mm, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-gen-params-final-run-train}: Training Phase}, coltitle=black, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, toprule=.15mm, opacityback=0, colback=white]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, left=2mm, opacitybacktitle=0.6, breakable, titlerule=0mm, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-gen-params-final-run-eval}: Evaluation Phase}, coltitle=black, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, toprule=.15mm, opacityback=0, colback=white]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, left=2mm, opacitybacktitle=0.6, breakable, titlerule=0mm, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-pen-final-run-train}: Training Phase}, coltitle=black, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, toprule=.15mm, opacityback=0, colback=white]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, left=2mm, opacitybacktitle=0.6, breakable, titlerule=0mm, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-pen-final-run-eval}: Evaluation Phase}, coltitle=black, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, toprule=.15mm, opacityback=0, colback=white]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, left=2mm, opacitybacktitle=0.6, breakable, titlerule=0mm, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-train-final-run-train}: Training Phase}, coltitle=black, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, toprule=.15mm, opacityback=0, colback=white]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, left=2mm, opacitybacktitle=0.6, breakable, titlerule=0mm, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-train-final-run-eval}: Evaluation Phase}, coltitle=black, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, toprule=.15mm, opacityback=0, colback=white]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, left=2mm, opacitybacktitle=0.6, breakable, titlerule=0mm, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-tune-train}: Training Phase}, coltitle=black, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, toprule=.15mm, opacityback=0, colback=white]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, left=2mm, opacitybacktitle=0.6, breakable, titlerule=0mm, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-tune-eval}: Evaluation Phase}, coltitle=black, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, toprule=.15mm, opacityback=0, colback=white]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, left=2mm, opacitybacktitle=0.6, breakable, titlerule=0mm, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-tune_lr-train}: Training Phase}, coltitle=black, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, toprule=.15mm, opacityback=0, colback=white]

@@

\begin{tcolorbox}[enhanced jigsaw, rightrule=.15mm, colbacktitle=quarto-callout-note-color!10!white, left=2mm, opacitybacktitle=0.6, breakable, titlerule=0mm, arc=.35mm, bottomrule=.15mm, colframe=quarto-callout-note-color-frame, title={Note \ref*{nte-tune_lr-eval}: Evaluation Phase}, coltitle=black, leftrule=.75mm, bottomtitle=1mm, toptitle=1mm, toprule=.15mm, opacityback=0, colback=white]

@@

We have taken care to set random seeds for reproducibility using Julia's
Random.jl package from the standard library. A global seed and (if
applicable or wanted) dataset-specific seeds can be specified in TOML
configuration files, environment variables or in interactive Julia
sessions. Additional details can be found in the code base.
